Models of lens candidates from Space Warps CFHTLS

### 2017-02-17 parts/massmodel.tex
editing

The mass distribution will naturally depend on the lens and source
redshifts, which are unknown when a lens candidate is first
identified.  But this is not a problem, because a model can be
trivially rescaled to use better redshift values, as and when they
become available.  This paper uses pipeline photometric redshifts for
the candidate lensing galaxies.  Source redshifts are set to $z=2$
unless an unambiguous photometric redshift is available.

@@

Figure~\ref{fig:encl} shows the circularly-averaged $\kappa$ of the
model ensemble, with increasing radius (in arcsec).  The effective
Einstein radius \ER is also shown.

Figure~\ref{fig:arriv}

Figure~\ref{fig:synth}
New method, see also Figure~\figref{synthimg} in
Appendix~\ref{subsec:sourcefit}.

>>>>

The mass will naturally depend on the lens and source redshifts, which
are unknown when a lens candidate is first identified.  But this is
not a problem, because a model can be trivially rescaled to use better
redshift values, as and when they become available.  This work applies
photometric redshifts from the CFHTLS pipeline to the candidate
lensing galaxies.  Source redshifts are set to $z=2$ unless an
unambiguous photometric redshift is available.

The ensemble of mass maps can be post-processed in many different
ways.  Four different graphical quantities are particularly useful.

Figure~\ref{fig:arriv} shows arrival-time surfaces corresponding to
the spaghetti diagrams in Figure~\ref{fig:splinput}.  The arrival-time
contours look like a machine-made elaborations of the input spaghetti
diagrams.  If the saddle-point contours in the arrival time are
qualitatively the same as the curves in the spaghetti diagram (the
detailed shape of the spaghetti curves is unimportant), it immediately
suggests a successful model.  On the other hand, if the arrival-time
surface has unexpected minima or saddle points, and especially if the
unexpected features are far from identified lens images, that signals
a doubtful model.  Figure~\ref{fig:synth} shows what we call synthetic
images, meaning reconstructions of the extended lensed features by
fitting for a source.  These were generated by new method, explained
in Appendix~\ref{subsec:sourcefit}, implemented in offline
post-processing after the modelling process was complete.  The
synthetic images provided by SpaghettiLens during the collaborative
modelling and discussion were more crude.

The arrival-time surface and synthetic image are summarised by one
diagnostic, the most important of all: are the lensed features
satisfactorily repoduced?  This diagnostic remains a judgement call by
modellers.  A useful quantitative criterion for whether the synthetic
image is consistent with the data would need to allow for PSF
dependence and unmodelled substructure ---otherwise all models would
be summarily rejected--- and it is not clear how to do this.

@@

Figure~\ref{fig:encl}. Appendix~\ref{subsec:hires} describes
improvements made since our earlier work \citep{2015MNRAS.447.2170K}
